%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}
\header{Chong }{Yun Long}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
+65 9852 0910
\href{mailto:chong.yunlong@gmail.com}{chong.yunlong@gmail.com}
~
\section{www}
\href{https://secure.flickr.com/photos/clouddra/}{flickr.com/clouddra}
\href{https://github.com/clouddra}{github.com/clouddra}
\href{https://sg.linkedin.com/in/chongyl}{linkedin.com/in/chongyl}
~
\section{languages}
english -- fluent
chinese[mandarin] -- fluent
japanese -- conversant
~
\section{programming}
C\#, Ruby
Typescript, JavaScript
Java, Python, 
C++, C, x86-64
Erlang
\LaTeX{}
~
\section{frameworks/libraries}
React.js
ASP.NET Core
Ruby on Rails, RSpec
Redux, Immutable.js
Android SDK, iOS SDK
%diStorm disassembler
~
%\section{tools}
%Webpack, Brakeman
%Burp Suite, mitmproxy
%IDA disassembler, QEMU
%~
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
%\begin{entrylist}
%------------------------------------------------
\entry
{\href{http://www.nus.edu.sg/}{National University of Singapore}}
{Aug 2010 \to June 2014}
{\emph{1st Class Honours in Bachelor of Computing, Computer Science}
\begin{itemize}
\item Dissertation (Applied Cryptography) -- \href{https://github.com/clouddra/FYP---Key-Aggregation/blob/master/paper/paper.pdf}{\emph{Efficient Key Aggregation for Cloud Storage}}
\item Specialization in Information Security, focus area in Parallel Computing
\item Awarded Dean's List for 3 semesters
\end{itemize}
}
%------------------------------------------------
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------
%\vspace{-2.2\parsep}
%\section{projects}
%\entrynormal{
%\begin{description}[style=unboxed,leftmargin=0cm, parsep=1.5pt]
%\item[WEP Cracker] Cryptanalysis attack on \href{https://en.wikipedia.org/wiki/RC4}{RC4 cipher} used in WEP
%\item[\href{https://github.com/sockmister/teach}{TeachMe!}] Social networking site which aims to bring together people with common interests
%\item[\href{https://github.com/clouddra/SPA}{SPA}] Static source code analyzer and parser
%\item[{\href{https://github.com/clouddra/Ethogram}{Ethogram}}] Android app which simplifies the process of cataloging and recording animal behavior
%\item[\href{https://github.com/clouddra/News-Butler}{News Butler}] Proof-of-concept Android news app which learns the preferences of user using data mining techniques
%\item[{\href{https://github.com/yzdong/impulsive-philanthropist-addon}{impulsive-philanthropist}}] Google Chrome extension that encourages people to make donations when making online purchases
%\end{description}
%}
\section{publications}
\entrysmall{\href{https://github.com/dkhungme/FastKAC}{Practical and Scalable Sharing of Encrypted Data in Cloud Storage with Key Aggregation}}{\href{http://ihmmsec.org/}{IH\&MMSec 2016}}
\entrysmall{\href{https://goo.gl/aFVeyy}{React Rails for Business Grants Portal}}{Medium}
%\end{description}
%}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}	
\entry
{\href{http://www.nutonomy.com/}{nuTonomy}}
{Jan 2015 \to Now}
{\emph{Software Engineer}
\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
\item Full stack developer (.NET Core/React) for shared services/mapping team.
\item Implemented tiling based three.js mesh garbage collector which improved frame rates of annotated maps by 300\%.
\item Introduced and coached the software team on Typescript/React. New CRUD services are written in Typescript/React and old services are incrementally rewritten using Typescript.
\item Built and pioneered various microservices (logs processsing, bookings, command center, computations) using modern .NET core on linux. Established coding standards for all backend microservices used in the company.
\item Set up one-command deployment procedures for all backend microservices by leverage on AWS cloud services(Elasticbeanstalk, Docker, Kinesis, Terraform). Uptime is higher and less error prone as compared to SSH-based deployments used previously.
\item Migrated log processing service from a single machine to a cloud-based service using streaming and reactive programming techniques (Rx.NET), resulting in improved reliability and scalability (processing thousands of car logs $\approx$1TB daily)
\item Set up company-wide authentication/authorization OAuth service using Auth0 to better protect company's intellectual property
\item Technology stack: ASP.NET Core MVC, Typscript, React, Redux, AWS Tools
\end{itemize}}

\entry
{\href{https://www.tech.gov.sg/}{Government Technology Agency of Singapore (GovTech)}}
{Jan 2015 \to Now}
{\emph{Product Engineer, Government Digital Services (GDS)}
\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
\item Ruby on Rails/React.js developer for Business Grant Portal (BGP) involving various government agencies.
\item Re-engineered the entire BGP frontend/backend into a single-page application to provide a slicker user experience and interface.
\item Established a unified architecture for BGP to reduce application complexity, improve code reusability, reliability and performanc.e
\item Set up dashboards (\href{http://grafana.org/}{Grafana}, \href{https://prometheus.io/}{Prometheus}) to visualize key business metrics and to monitor system performance.
\item Mentored and coached the team, new hires and vendors on the latest open source technologies.
\item Employed modern software development methodologies and techniques (scrum, test-driven development, pair programming) to deliver quality products with high business value. 
\end{itemize}}

\entry
{\href{https://www.dso.org.sg/}{DSO National Laboratories}}
{July 2014 \to Jan 2015}
{\emph{Member of Technical Staff, Computer Security Lab}
\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
\item Analyzed protection mechanisms of Microsoft Windows kernel
\item Researched novel reverse engineering techniques using emulators and virtualization technologies
\item Conducted network security research on NAT networks
\item If I told you more I would have to kill you \dots
\end{itemize}}
%\begin{entrylist}
%------------------------------------------------
\entry
{\href{http://www.shoppink.me/}{TADA Pte Ltd}}
{May 2013 \to Aug 2013}
{\emph{Mobile Development Intern}
\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
\item Independently picked up iOS and Android development concepts within a period of 3 months.
\item Developed \href{http://www.shoppink.me/}{\emph{Shoppink}} (Android, 2 months) -- mobile e-commerce platform for blogshops. Shoppink uses a specialized algorithm to tracks products from over 200 blogshops.
\item Developed \href{http://www.shoppink.me/tomyself}{\emph{ToMyself}} (iOS, 1 month) -- mailer app designed for users who frequently send emails to themselves. \emph{ToMyself} is available on App Store.
\end{itemize}}
%------------------------------------------------
%\entry
%{\href{http://www.rgei.com/}{RGE Pte Ltd}}
%{May 2011 \to July 2011}
%{\emph{Summer Intern}
%\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
%\item Collaborated extensively with overseas team members for the development and testing of corporate dashboard, which presents raw data in a visually meaningful way, assisting the top management in their decision making process 
%\item Assisted in the deployment of IT infrastructure for more than 100 staff in a newly renovated office
%\item Provided IT support for more than 300 end users, expediting the resolution of any technical problems faced so as to minimize disruption to their business
%\item Supported server and blackberry administration
%\end{itemize}}
%------------------------------------------------
%\entry
%{\href{http://www.ncs.com.sg/}{NCS Pte Ltd}}
%{Nov 2009 -- May 2010}
%{\emph{Temporary Staff, Chief Architect Office}
%\begin{itemize}[topsep=2.5pt, parsep=1.5pt]
%\item Collaborated with a team of consultants of different nationalities for a multi-million dollar government project.
%\item Assisted analysts in the design and coding of the mockups, giving clients a visual experience, allowing them to give better feedback on the system and helps streamlines the requirements gathering process.
%\item Developed a prototype as an illustrative reference for offshore. development teams who may have difficulties understanding the specifications due to language barriers.
%\end{itemize}
%}
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{certifications}
\entrysmall
{\href{https://www.iss.nus.edu.sg/ProfessionalCourses/SearchCourse/CourseDetail/tabid/267/cid/399/cname/lean-kanban-foundation/Default.aspx}{Kanban Management Professional - I}}
{Jun 2016 \to Now}
\entrysmall
{\href{http://securitystartshere.org/page-training-oswap.htm}{Organizational Systems Web Application Pentester}}
{Apr 2015 \to Now}
\entrysmall
{\href{https://www.scrumalliance.org/certifications/practitioners/certified-scrummaster-csm}{Certified ScrumMaster}}
{Apr 2015 \to Apr 2017}
%%----------------------------------------------------------------------------------------
%%	CO-CURRICULAR SKILLS SECTION
%%----------------------------------------------------------------------------------------
%\vspace{-2.2\parsep}
%\section{co-curricular}
%\entry
%{\href{http://www.sg.emb-japan.go.jp/culture_kizuna.htm}{Kizuna Project}}
%{Jul 2012}
%{\emph{Cultural exchange program to Japan}
%\begin{itemize}
%\item Gained awareness of Japan's post-earthquake revival efforts as well as the economic and social impact the earthquake had on Fukushima 
%\item Created a \href{http://courseware.nus.edu.sg/e-raion/document/KIZUNA/ChongYunLongPhotobook.pdf}{photobook} and a \href{http://courseware.nus.edu.sg/e-raion/document/KIZUNA/ChongYunLongReport.pdf}{report} to share my experiences on the trip and to educate the public about the post-earthquake situation in Fukushima 
%\end{itemize}
%}


%\entry
%{\href{http://www.mindef.gov.sg/imindef/home.html}{National Service. MINDEF Medical Centre (MMC)}}
%{Jan 2008 -- Nov 2009}
%{\emph{Combat Medic, Registration/Appointment IC}
%\begin {itemize}
%\item Managed and supervised the registration and administration section of MMC
%\item Revamped registration and administration workflow, which help improved customer experience and alleviating unnecessary waiting
%\item Spearheaded the design of a standardized emergency drug manual and was awarded silver in WITs competition
%\item Received commendation from various officers throughout my stint in MMC
%\end{itemize}
%}

%\entry
%{\href{http://www.simtech.a-star.edu.sg/}{A*STAR (SIMTech)}}
%{Nov 2006 -- Dec 2006}
%{\emph{Research Intern}
%\begin {itemize}
%\item Worked in a team of research scientists for an A*STAR-Rolls Royce collaboration project.
%\item Calibrated and programmed an industrial gantry robot used for fuel cell assembly
%\item Contributed ideas to the design of the gantry robot
%\end{itemize}
%}

\end{document}